Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-02-06 man/figures/gc_perc_trees.Rmd
add legend labels

pgc_median50 <- gc_treesMed50 %>% 
  filter(total_tree > 2) %>% 
  ggplot() +
  geom_bar(aes(x=year, y=per_pos), fill=colorpositivo, colour=colorpositivo, 
           stat = "identity", position = "dodge") + 
  geom_bar(aes(x=year, y=(-1)*per_neg), fill=colornegativo, colour=colornegativo, 
           stat = "identity", position = "dodge") +
  geom_line(aes(x=year, y=total_tree), colour = 'black', size = 0.4) + 
  theme_bw() + ylab('% of trees') + xlab("Year") + 
  geom_hline(yintercept=0, alpha=.4) +
  geom_hline(yintercept=c(50, -50), linetype=2, alpha=.4) +
  scale_x_continuous(breaks = xrange) +
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 50),
                     sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  facet_rep_wrap(~site_sorted, nrow = 3, 
                 repeat.tick.labels = TRUE, labeller = as_labeller(label_site)) +
  theme(panel.grid = element_blank(), 
        strip.background = element_blank(), 
        strip.text = element_blank(),
        axis.text.y.left = element_text(size=6),
        axis.text.y.right  = element_text(size=5),
        axis.text.x = element_text(size=6),
        axis.title = element_text(size = 9))

>>>>

pgc_median50 <- gc_treesMed50 %>% 
  filter(total_tree > 2) %>% 
  ggplot() +
  geom_bar(aes(x=year, y=per_pos), fill=colorpositivo, colour=colorpositivo, 
           stat = "identity", position = "dodge") + 
  geom_bar(aes(x=year, y=(-1)*per_neg), fill=colornegativo, colour=colornegativo, 
           stat = "identity", position = "dodge") +
  geom_line(aes(x=year, y=total_tree*2), colour = 'black', size = 0.2) + 
  theme_bw() + ylab('% of trees') + xlab("Year") + 
  geom_hline(yintercept=0, alpha=.4) +
  geom_hline(yintercept=c(50, -50), linetype=2, alpha=.4) +
  scale_x_continuous(breaks = xrange) +
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, by = 50),
                     sec.axis = sec_axis(~., name = '# trees', breaks = c(0,15,30))) +
  facet_rep_wrap(~site_sorted, nrow = 3, 
                 repeat.tick.labels = TRUE, labeller = as_labeller(label_site)) +
  theme(panel.grid = element_blank(), 
        strip.background = element_blank(), 
        strip.text = element_text(face = "bold", size = 12),
        strip.placement = "inside", 
        axis.text.y.left = element_text(size=6),
        axis.text.y.right  = element_text(size=5),
        axis.text.x = element_text(size=6),
        axis.title = element_text(size = 9))
